---
title: "placeholder"
always_allow_html: true
output: 
  officedown::rdocx_document:
    reference_docx: tbl_shell.docx
    keep_md: true
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE,
                      warning = FALSE,
                      dpi = 600, 
                      fig.width = 11, 
                      fig.height = 6)

library(table.glue)
library(officer)
library(flextable)
library(janitor)
library(tidyverse)

conflicted::conflicts_prefer(flextable::as_flextable)

table_polisher <- function(ft,
                           font_size = 11,
                           font_name = "Calibri"){

  ft %>%
    font(fontname = font_name, part = 'all') %>%
    fontsize(size = font_size, part = 'all') %>%
    height(height = 2, part = 'footer')

}

# specification for table tables
rspec <- round_spec() |>
  round_using_magnitude(digits = c(2, 1),
                        breaks = c(2, Inf))

# rspec <- round_spec() |>
#   round_using_decimal(digits = 1)

# save it to options:
names(rspec) <- paste('table.glue', names(rspec), sep = '.')
options(rspec)

# default is double space 
# single spacing for title page, abstract, captions
single_par <- fp_par(line_spacing=1)

fts <- c(
    '\u2A',
    '\u2020',
    '\u2021',
    '\uA7',
    '\u2016',
    '\uB6',
    '#',
    '\u2a\u2a',
    '\u2020\u2020',
    '\u2021\u2021'
  )

bp_cat_descr <- "SBP/DBP categories in mm Hg among US adults not taking antihypertensive medication"

```

Byron C. Jaeger, PhD,^1^ 

^1^Department of Biostatistics and Data Science, Wake Forest School of Medicine, Winston-Salem, NC. `r single_par`

```{r load-targets, include=FALSE}

withr::with_dir(here::here(),code = {
 targets::tar_load(names = c(nhanes_excluded,
                             analysis_overall,
                             analysis_comorb)) 
})

```

\newpage

Table: Exclusions

```{r}

nhanes_excluded$counts %>% 
  flextable() %>% 
  theme_box() %>% 
  set_header_labels(
    'label' = 'Inclusion criteria',
    overall = "Total"
  ) %>% 
  width(width = 1.25) %>%
  width(j = 2:5, width = 1.1) %>% 
  align(align = 'center', part = 'all') %>%
  align(j = 1, align = 'left', part = 'all') %>% 
  table_polisher()

```


\newpage

Table 1. Characteristics of US adults by blood pressure levels and antihypertensive medication use based on the 2013-2020 National Health and Nutrition Examination Survey.  

```{r}

value_note <-  
  "Population characteristics in the table are percentage or mean (95% confidence interval)."

bp_note <- 
  "US adults were grouped into the higher category of systolic and diastolic blood pressure. For example, if a person had systolic blood pressure of 146 mm Hg and diastolic blood pressure of 82 mm Hg, they were grouped into the ≥140/90 mm Hg category."

abbrvs <- "SBP – systolic blood pressure; DBP – diastolic blood pressure; eGFR - estimated glomerular filtration rate."

tbl <- analysis_overall %>% 
  getElement("tbl_characteristics_overall") %>% 
  getElement("bpcat")


tbl %>% 
  as_grouped_data(groups = 'label') %>%
  remove_empty('rows') %>%
  add_row(label = "Characteristics", .after = 2) %>% 
  as_flextable(hide_grouplabel = TRUE) %>%
  add_header_row(
    values = c("", bp_cat_descr, names(tbl)[7]), 
    colwidths = c(1, 4, 1)
  ) %>%
  theme_box() %>%
  set_header_labels(
    'level' = ' '
  ) %>%
  padding(i = 7:12, j = 1, padding.left = 10, part = 'body') %>%
  height(height = 1.5, part = 'header') %>%
  width(width = 1.25) %>%
  width(j = 2:5, width = 1.1) %>% 
  align(align = 'center', part = 'all') %>%
  align(j = 1, align = 'left', part = 'all') %>%
  footnote(
    i = 3,
    j = 1,
    part = 'body',
    value = as_paragraph(value_note),
    ref_symbols = fts[2]
  ) %>%
  footnote(i = 1, 
           j = 2, 
           part = 'header',
           value = as_paragraph(bp_note),
           ref_symbols = fts[1]) %>% 
  add_footer_lines(value = as_paragraph(abbrvs)) %>%
  merge_v(part = 'header') %>%
  table_polisher()

```

\newpage

Table 2. Ten-year predicted cardiovascular disease risk by blood pressure levels and antihypertensive medication use based on the 2013-2020 National Health and Nutrition Examination Survey.  

```{r}

tbl <- analysis_overall %>% 
  getElement("tbl_risk_means_overall")

tbl %>% 
  as_grouped_data(groups = 'outcome') %>%
  as_flextable(hide_grouplabel = TRUE) %>% 
  add_header_row(
    values = c("", bp_cat_descr, names(tbl)[7]), 
    colwidths = c(1, 4, 1)
  ) %>% 
  theme_box() %>% 
  set_header_labels(
    'label' = 'Mean (95% CI) 10-year predicted risk'
  ) %>% 
  padding(i = 2:4, j = 1, padding.left = 10, part = 'body') %>%
  padding(i = 6:7, j = 1, padding.left = 10, part = 'body') %>%
  height(height = 1.5, part = 'header') %>%
  width(width = 1.25) %>%
  width(j = 2:5, width = 1.1) %>% 
  align(align = 'center', part = 'all') %>%
  align(j = 1, align = 'left', part = 'all') %>%
  # add_footer_lines(value = as_paragraph(abbrvs)) %>% 
  merge_v(part = 'header') %>% 
  table_polisher()

```

\newpage

Table 3. Distribution of 10-year predicted risk by blood pressure levels and antihypertensive medication use based on the 2013-2020 National Health and Nutrition Examination Survey. 

```{r}

tbl <- analysis_overall %>% 
  getElement("tbl_risk_dist_overall")

tbl %>% 
  as_grouped_data(groups = 'label') %>%
  as_flextable(hide_grouplabel = TRUE) %>% 
  add_header_row(
    values = c("", bp_cat_descr,  names(tbl)[7]), 
    colwidths = c(1, 4, 1)
  ) %>% 
  theme_box() %>% 
  set_header_labels(
    'risk_cat' = '10-year risk categories, %'
  ) %>% 
  padding(i = ~is.na(label), j = 1, padding.left = 10, part = 'body') %>% 
  height(height = 1.5, part = 'header') %>%
  width(width = 1.25) %>%
  width(j = 2:5, width = 1.1) %>% 
  align(align = 'center', part = 'all') %>%
  align(j = 1, align = 'left', part = 'all') %>%
  # add_footer_lines(value = as_paragraph(abbrvs)) %>% 
  merge_v(part = 'header') %>% 
  table_polisher()

```

<!-- new page not needed at the end of a block section -->
```{r}

margins_normal <- page_mar(bottom = 2.54 * 0.3937, 
                           top    = 2.54 * 0.3937, 
                           right  = 2.54 * 0.3937, 
                           left   = 2.54 * 0.3937,
                           gutter = 0)

# block_section(
#   prop_section(
#     page_size = page_size(orient = "portrait"),
#     type = "continuous",
#     page_margins = margins_normal
#   )
# )

```

\newpage

Table 4. Cross-categorization of 10-year predicted risk by the PREVENT and pooled cohort equations based on the 2013-2020 National Health and Nutrition Examination Survey.

```{r}

tbl_overall <- analysis_overall %>% 
  getElement("tbl_risk_cross_overall") %>% 
  getElement("overall")

tbl_overall_by_age <- analysis_overall %>% 
  getElement("tbl_risk_cross_overall") %>% 
  getElement("by_age")

tbl_comorb <- analysis_comorb %>% 
  getElement("tbl_risk_cross_comorb") %>% 
  getElement("overall")


tbls_risk_cross <- list(
  overall = tbl_overall,
  overall_by_age = tbl_overall_by_age,
  comorb = tbl_comorb
) %>% 
  map(
    .f = function(tbl){
      tbl %>% 
        as_grouped_data(groups = 'label') %>%
        as_flextable(hide_grouplabel = TRUE) %>% 
        add_header_row(
          values = c("", bp_cat_descr, names(tbl)[8]), 
          colwidths = c(2, 4, 1)
        ) %>% 
        theme_box() %>% 
        set_header_labels(
          'left_var' = 'PCE',
          'right_var' = 'PREVENT'
        ) %>% 
        padding(i = ~is.na(label), 
                j = 1, 
                padding.left = 10, 
                part = 'body') %>% 
        height(height = 1.5, part = 'header') %>%
        width(width = 1.25) %>%
        width(j = 1:6, width = 1.1) %>% 
        align(align = 'center', part = 'all') %>%
        align(j = 1, align = 'left', part = 'all') %>%
        # add_footer_lines(value = as_paragraph(abbrvs)) %>% 
        merge_v(part = 'header') %>% 
        table_polisher()
    })

tbls_risk_cross$overall

```

\newpage

Table 4 Sensitivity analysis: Cross-categorization of 10-year predicted risk by the PREVENT and pooled cohort equations based on the 2013-2020 National Health and Nutrition Examination Survey after excluding people age ≥65 years, with diabetes or chronic kidney disease (ACR > 30 mg/g or eGFR < 60 ml/min/1.73 m^2^).

```{r}
tbls_risk_cross$comorb
```

\newpage

Table 4 stratified by age. Cross-categorization of 10-year predicted risk by the PREVENT and pooled cohort equations based on the 2013-2020 National Health and Nutrition Examination Survey.

```{r}

tbls_risk_cross$overall_by_age

```

\newpage

```{r}
# block_section(
#   prop_section(
#     page_size = page_size(orient = "landscape"),
#     page_margins = page_mar(bottom = 1/8, top = 1/8, 
#                             right = 1/4, left = 1/4),
#     type = "continuous"
#   )
# )
```

Table 5: Characteristics of US adults with SBP of 130-139 mm Hg or DBP of 80-89 mm Hg by predicted risk use based on the 2013-2020 National Health and Nutrition Examination Survey

```{r}

tbl <- analysis_overall %>% 
  getElement("tbl_discrepant_overall")

tbl %>% 
  as_grouped_data(groups = 'label') %>%
  remove_empty('rows') %>% 
  as_flextable(hide_grouplabel = TRUE) %>% 
  add_header_row(
    values = c(" ", "Prevalence ratio (95% CI)"),
               colwidths = c(3, 2)
  ) %>%
  theme_box() %>% 
  set_header_labels(
    level = "Characteristic",
    'pr_unadj' = 'Unadjusted',
    'pr_adj' = 'Adjusted'
  ) %>% 
  padding(i = 4:8, j = 1, 
          padding.left = 10, 
          part = 'body') %>% 
  height(height = 1.5, part = 'header') %>%
  width(width = 1.1) %>%
  align(align = 'center', part = 'all') %>%
  align(j = 1, align = 'left', part = 'all') %>%
  # add_footer_lines(value = as_paragraph(abbrvs)) %>% 
  merge_v(part = 'header') %>% 
  footnote(
    i = 2,
    j = 1,
    part = 'header',
    value = as_paragraph(value_note),
    ref_symbols = fts[2]
  ) %>% 
  footnote(
    i = 2, 
    j = 5, 
    value = as_paragraph("Adjusted for age and sex."),
    ref_symbols = fts[3],
    part = 'header'
  ) %>% 
  table_polisher()

```

```{r}
block_section(
  prop_section(
    page_size = page_size(orient = "portrait"),
    type = "continuous",
    page_margins = margins_normal
  )
)
```

Table 6: Characteristics of US adults by BP category and predicted risk use based on the 2013-2020 National Health and Nutrition Examination Survey.

```{r}

tbl <- analysis_overall %>% 
  getElement("tbl_characteristics_overall") %>% 
  getElement('bpcat_discrep')

tbl %>% 
  as_grouped_data(groups = 'label') %>%
  remove_empty('rows') %>%
  as_flextable(hide_grouplabel = TRUE) %>%
  add_header_row(
    values = c("",
               "<120/80", 
               "120-129/<80", 
               "130-139/80-89", 
               "≥140/90", 
               "Taking antihypertensive medication"), 
    colwidths = c(1, 2, 2, 2, 2, 2)
  ) %>%
  theme_box() %>%
  set_header_labels(
    level = "Characteristic",
    hi_lo_lt_120 = "PCE ≥ 10% PREVENT < 15%",
    hi_hi_lt_120 = "PCE ≥ 10% PREVENT ≥ 15%",
    hi_lo_lt_130 = "PCE ≥ 10% PREVENT < 15%",
    hi_hi_lt_130 = "PCE ≥ 10% PREVENT ≥ 15%",
    hi_lo_lt_140 = "PCE ≥ 10% PREVENT < 15%",
    hi_hi_lt_140 = "PCE ≥ 10% PREVENT ≥ 15%",
    hi_lo_gteq_140 = "PCE ≥ 10% PREVENT < 15%",
    hi_hi_gteq_140 = "PCE ≥ 10% PREVENT ≥ 15%",
    hi_lo_meds = "PCE ≥ 10% PREVENT < 15%",
    hi_hi_meds = "PCE ≥ 10% PREVENT ≥ 15%"
  ) %>%
  padding(i = 4:8, j = 1, padding.left = 10, part = 'body') %>%
  height(height = 1.5, part = 'header') %>%
  width(width = 1) %>% 
  width(j = 1, width = 1.3) %>%
  align(align = 'center', part = 'all') %>%
  align(j = 1, align = 'left', part = 'all') %>%
  footnote(
    i=2, j=1, part='header', 
    value=as_paragraph(value_note), 
    ref_symbols=fts[2]) %>%
  add_footer_lines(
    value = as_paragraph(abbrvs)
  ) %>% 
  merge_v(part = 'header') %>% 
  table_polisher()

```



```{r}
block_section(
  prop_section(
    page_size = page_size(orient = "landscape"),
    page_margins = page_mar(bottom = 1/8, top = 1/8, 
                            right = 1/4, left = 1/4),
    type = "continuous"
  )
)
```
