---
title: "placeholder"
always_allow_html: true
output: 
  officedown::rdocx_document:
    reference_docx: tbl_shell.docx
    keep_md: true
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE,
                      warning = FALSE,
                      dpi = 600, 
                      fig.width = 11, 
                      fig.height = 6)

library(table.glue)
library(officer)
library(flextable)
library(janitor)

conflicted::conflicts_prefer(flextable::as_flextable)

table_polisher <- function(ft,
                           font_size = 11,
                           font_name = "Calibri"){

  ft %>%
    font(fontname = font_name, part = 'all') %>%
    fontsize(size = font_size, part = 'all') %>%
    height(height = 2, part = 'footer')

}

# specification for table tables
rspec <- round_spec() |>
  round_using_magnitude(digits = c(2, 1),
                        breaks = c(2, Inf))

# rspec <- round_spec() |>
#   round_using_decimal(digits = 1)

# save it to options:
names(rspec) <- paste('table.glue', names(rspec), sep = '.')
options(rspec)

# default is double space 
# single spacing for title page, abstract, captions
single_par <- fp_par(line_spacing=1)

fts <- c(
    '\u2A',
    '\u2020',
    '\u2021',
    '\uA7',
    '\u2016',
    '\uB6',
    '#',
    '\u2a\u2a',
    '\u2020\u2020',
    '\u2021\u2021'
  )


```

Byron C. Jaeger, PhD,^1^ 

^1^Department of Biostatistics and Data Science, Wake Forest School of Medicine, Winston-Salem, NC. `r single_par`

```{r load-targets, include=FALSE}

withr::with_dir(here::here(),code = {
 targets::tar_load(names = c(tbl_characteristics,
                             tbl_risk_means,
                             tbl_risk_distr,
                             tbl_risk_cross)) 
})

```

\newpage

Table 1. Characteristics of US adults by blood pressure levels and antihypertensive medication use based on the 2013-2020 National Health and Nutrition Examination Survey.  

```{r}

value_note <-  
  "Population characteristics in the table are percentage or mean (95% confidence interval). US adults were grouped into the higher category of systolic and diastolic blood pressure. For example, if a person had systolic blood pressure of 146 mm Hg and diastolic blood pressure of 82 mm Hg, they were grouped into the ≥140/90 mm Hg category."

abbrvs <- "SBP – systolic blood pressure; DBP – diastolic blood pressure; eGFR - estimated glomerular filtration rate."


tbl_characteristics %>% 
  as_grouped_data(groups = 'label') %>%
  remove_empty('rows') %>%
  as_flextable(hide_grouplabel = TRUE) %>%
  add_header_row(
    values = c("", 
               "SBP/DBP categories in mm Hg among US adults not taking antihypertensive medication", 
               names(tbl_characteristics)[7]), 
                 colwidths = c(1, 4, 1)
  ) %>%
  theme_box() %>%
  set_header_labels(
    'level' = 'Characteristic'
  ) %>%
  padding(i = 4:9, j = 1, padding.left = 10, part = 'body') %>%
  height(height = 1.5, part = 'header') %>%
  width(width = 1.25) %>%
  width(j = 2:5, width = 1.1) %>% 
  align(align = 'center', part = 'all') %>%
  align(j = 1, align = 'left', part = 'all') %>%
  footnote(
    i=2, j=1, part='header', 
    value=as_paragraph(value_note), 
    ref_symbols=fts[2]) %>%
  add_footer_lines(
    value = as_paragraph(abbrvs)
  ) %>% 
  merge_v(part = 'header') %>% 
  table_polisher()

```

\newpage

Table 2. Ten-year predicted cardiovascular disease risk by blood pressure levels and antihypertensive medication use based on the 2013-2020 National Health and Nutrition Examination Survey.  

```{r}

tbl_risk_means %>% 
  as_grouped_data(groups = 'outcome') %>%
  as_flextable(hide_grouplabel = TRUE) %>% 
  add_header_row(
    values = c("", 
               "SBP/DBP categories in mm Hg among US adults not taking antihypertensive medication", 
               names(tbl_risk_means)[7]), 
                 colwidths = c(1, 4, 1)
  ) %>% 
  theme_box() %>% 
  set_header_labels(
    'label' = 'Mean (95% CI) 10-year predicted risk'
  ) %>% 
  padding(i = 2:4, j = 1, padding.left = 10, part = 'body') %>%
  padding(i = 6:7, j = 1, padding.left = 10, part = 'body') %>%
  height(height = 1.5, part = 'header') %>%
  width(width = 1.25) %>%
  width(j = 2:5, width = 1.1) %>% 
  align(align = 'center', part = 'all') %>%
  align(j = 1, align = 'left', part = 'all') %>%
  # add_footer_lines(value = as_paragraph(abbrvs)) %>% 
  merge_v(part = 'header') %>% 
  table_polisher()

```

\newpage

Table 3. Distribution of 10-year predicted risk by blood pressure levels and antihypertensive medication use based on the 2013-2020 National Health and Nutrition Examination Survey. 

```{r}

tbl_risk_distr %>% 
  as_grouped_data(groups = 'label') %>%
  as_flextable(hide_grouplabel = TRUE) %>% 
  add_header_row(
    values = c("", 
               "SBP/DBP categories in mm Hg among US adults not taking antihypertensive medication", 
               names(tbl_risk_distr)[7]), 
                 colwidths = c(1, 4, 1)
  ) %>% 
  theme_box() %>% 
  set_header_labels(
    'risk_cat' = '10-year risk categories, %'
  ) %>% 
  padding(i = ~is.na(label), j = 1, padding.left = 10, part = 'body') %>% 
  height(height = 1.5, part = 'header') %>%
  width(width = 1.25) %>%
  width(j = 2:5, width = 1.1) %>% 
  align(align = 'center', part = 'all') %>%
  align(j = 1, align = 'left', part = 'all') %>%
  # add_footer_lines(value = as_paragraph(abbrvs)) %>% 
  merge_v(part = 'header') %>% 
  table_polisher()

```

<!-- new page not needed at the end of a block section -->
```{r}

margins_normal <- page_mar(bottom = 2.54 * 0.3937, 
                           top    = 2.54 * 0.3937, 
                           right  = 2.54 * 0.3937, 
                           left   = 2.54 * 0.3937,
                           gutter = 0)

block_section(
  prop_section(
    page_size = page_size(orient = "portrait"),
    type = "continuous",
    page_margins = margins_normal
  )
)

```

Table 4. Cross-categorization of 10-year predicted risk by the PREVENT and pooled cohort equations based on the 2013-2020 National Health and Nutrition Examination Survey.

```{r}

tbl_risk_cross %>% 
  as_grouped_data(groups = 'label') %>%
  as_flextable(hide_grouplabel = TRUE) %>% 
  add_header_row(
    values = c("", 
               "SBP/DBP categories in mm Hg among US adults not taking antihypertensive medication", 
               names(tbl_risk_distr)[7]), 
                 colwidths = c(2, 4, 1)
  ) %>% 
  theme_box() %>% 
  set_header_labels(
    'left_var' = 'PREVENT',
    'right_var' = 'PCE'
  ) %>% 
  padding(i = ~is.na(label), j = 1, padding.left = 10, part = 'body') %>% 
  height(height = 1.5, part = 'header') %>%
  width(width = 1.25) %>%
  width(j = 1:6, width = 1.1) %>% 
  align(align = 'center', part = 'all') %>%
  align(j = 1, align = 'left', part = 'all') %>%
  # add_footer_lines(value = as_paragraph(abbrvs)) %>% 
  merge_v(part = 'header') %>% 
  table_polisher()

```

```{r}
block_section(
  prop_section(
    page_size = page_size(orient = "landscape"),
    page_margins = page_mar(bottom = 1/8, top = 1/8, 
                            right = 1/4, left = 1/4),
    type = "continuous"
  )
)
```
