---
title: "placeholder"
always_allow_html: true
output: 
  officedown::rdocx_document:
    reference_docx: tbl_shell.docx
    keep_md: true
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE,
                      warning = FALSE,
                      dpi = 600, 
                      fig.width = 11, 
                      fig.height = 6)

library(table.glue)
library(officer)
library(flextable)
library(janitor)
library(tidyverse)

conflicted::conflicts_prefer(flextable::as_flextable)
conflicted::conflicts_prefer(dplyr::filter)

# specification for table tables
rspec <- round_spec() |>
  round_using_magnitude(digits = c(1, 0), breaks = c(100, Inf))

# rspec <- round_spec() |>
#   round_using_decimal(digits = 1)

# save it to options:
names(rspec) <- paste('table.glue', names(rspec), sep = '.')
options(rspec)

table_polisher <- function(ft,
                           font_size = 11,
                           font_name = "Arial"){

  ft %>%
    font(fontname = font_name, part = 'all') %>%
    fontsize(size = font_size, part = 'all') %>%
    height(height = 2, part = 'footer')

}

# default is double space 
# single spacing for title page, abstract, captions
single_par <- fp_par(line_spacing=1)

fts <- c(
    '\u2A',
    '\u2020',
    '\u2021',
    '\uA7',
    '\u2016',
    '\uB6',
    '#',
    '\u2a\u2a',
    '\u2020\u2020',
    '\u2021\u2021'
  )

bp_cat_descr <- "SBP/DBP categories in mm Hg among US adults not taking antihypertensive medication"

```

Byron C. Jaeger, PhD,^1^ 

^1^Department of Biostatistics and Data Science, Wake Forest School of Medicine, Winston-Salem, NC. `r single_par`

```{r load-targets, include=FALSE}

withr::with_dir(here::here(),code = {
 targets::tar_load(names = c(nhanes_excluded,
                             analysis_overall,
                             analysis_comorb,
                             analysis_lt60)) 
})

```

\newpage

Table 1. Characteristics of US adults by blood pressure levels and antihypertensive medication use based on the 2013-2020 National Health and Nutrition Examination Survey.  

```{r}

value_note <-  
  "Population characteristics in the table are percentage or mean (95% confidence interval). For albumin-to-creatinine ratio, the table value is median (95% confidence interval)."

bp_note <- 
  "US adults were grouped into the higher category of systolic and diastolic blood pressure. For example, if a person had systolic blood pressure of 146 mm Hg and diastolic blood pressure of 82 mm Hg, they were grouped into the ≥140/90 mm Hg category."

abbrvs <- "ACR – albumin to creatinine ratio; DBP – diastolic blood pressure; eGFR – estimated glomerular filtration rate. HDL – high density lipoprotein; SBP – systolic blood pressure"

tbl <- analysis_overall %>% 
  getElement("tbl_characteristics_overall") %>% 
  getElement("bpcat")


tbl %>% 
  as_grouped_data(groups = 'label') %>%
  remove_empty('rows') %>%
  # add_row(label = "Characteristics", .after = 1) %>% 
  as_flextable(hide_grouplabel = TRUE) %>%
  add_header_row(
    values = c("", bp_cat_descr, names(tbl)[7]), 
    colwidths = c(1, 4, 1)
  ) %>%
  theme_box() %>%
  set_header_labels(
    'level' = 'Characteristic'
  ) %>%
  padding(i = 4:8, j = 1, padding.left = 10, part = 'body') %>%
  height(height = 1.5, part = 'header') %>%
  width(width = 1.25) %>%
  width(j = 2:5, width = 1.1) %>% 
  align(align = 'center', part = 'all') %>%
  align(j = 1, align = 'left', part = 'all') %>%
  footnote(
    i = 2,
    j = 1,
    part = 'header',
    value = as_paragraph(value_note),
    ref_symbols = fts[2]
  ) %>%
  footnote(i = 1, 
           j = 2, 
           part = 'header',
           value = as_paragraph(bp_note),
           ref_symbols = fts[1]) %>% 
  add_footer_lines(value = as_paragraph(abbrvs)) %>%
  merge_v(part = 'header') %>%
  table_polisher()

```

\newpage

Table 2. Distribution of 10-year predicted risk by blood pressure levels and antihypertensive medication use based on the 2013-2020 National Health and Nutrition Examination Survey. 

```{r}


tbl_means <- analysis_overall %>% 
  getElement("tbl_risk_means_overall") %>% 
  mutate(risk_cat = "Mean\n(95% CI)",
         label = paste(label, outcome, sep = ' - ')) %>% 
  select(-outcome)

tbl_distr <- analysis_overall %>% 
  getElement("tbl_risk_dist_overall")

tbl_dist_base <- 
  bind_rows(tbl_means, tbl_distr) %>% 
  filter(!str_detect(label, "full")) 

tbl_dist_full <- 
  bind_rows(tbl_means, tbl_distr) %>% 
  filter(!str_detect(label, "base")) 


tbls_dist <- list(main = tbl_dist_base,
                  supp = tbl_dist_full) %>% 
  map(
    ~ .x %>% 
      mutate(
        label = factor(label),
        label = relevel(label, ref = "Pooled cohort equations - ASCVD")
      ) %>% 
      arrange(label) %>% 
      relocate(risk_cat, .before = 2) %>% 
      as_grouped_data(groups = 'label') %>%
      as_flextable(hide_grouplabel = TRUE) %>% 
      add_header_row(
        values = c("", bp_cat_descr, names(.x)[6]), 
        colwidths = c(1, 4, 1)
      ) %>% 
      theme_box() %>% 
      set_header_labels(
        'risk_cat' = 'Distribution characteristic'
      ) %>% 
      padding(i = ~ is.na(label), j = 1, padding.left = 10, part = 'body') %>%
      height(height = 1.5, part = 'header') %>%
      width(width = 1.25) %>%
      width(j = 2:5, width = 1.1) %>% 
      align(align = 'center', part = 'all') %>%
      align(j = 1, align = 'left', part = 'all') %>%
      # add_footer_lines(value = as_paragraph(abbrvs)) %>% 
      merge_v(part = 'header') %>% 
      table_polisher()
    
  )

tbls_dist$main

```

<!-- new page not needed at the end of a block section -->
```{r}

margins_normal <- page_mar(bottom = 2.54 * 0.3937, 
                           top    = 2.54 * 0.3937, 
                           right  = 2.54 * 0.3937, 
                           left   = 2.54 * 0.3937,
                           gutter = 0)

block_section(
  prop_section(
    page_size = page_size(orient = "portrait"),
    type = "continuous",
    page_margins = margins_normal
  )
)

```

Table 3. Cross-categorization of 10-year predicted risk by the PREVENT and pooled cohort equations based on the 2013-2020 National Health and Nutrition Examination Survey.

```{r}

tbl_overall <- analysis_overall %>% 
  getElement("tbl_risk_cross_overall") %>% 
  getElement("overall")

tbl_lt60_30 <- analysis_lt60 %>% 
  getElement("tbl_risk_cross_age_lt60") %>% 
  getElement("overall_30") %>% 
  relocate(pce_var, .before = prevent_var)

tbl_overall_by_age <- analysis_overall %>% 
  getElement("tbl_risk_cross_overall") %>% 
  getElement("by_age")

tbl_comorb <- analysis_comorb %>% 
  getElement("tbl_risk_cross_comorb") %>% 
  getElement("overall")


tbls_risk_cross <- list(
  
  overall_base = filter(tbl_overall, !str_detect(label, 'full')),
  lt60_30_base = filter(tbl_lt60_30, !str_detect(label, 'full')),
  overall_by_age_base = filter(tbl_overall_by_age, !str_detect(label, 'full')),
  comorb_base = filter(tbl_comorb, !str_detect(label, 'full')),
  
  overall_full = filter(tbl_overall, !str_detect(label, 'base')),
  lt60_30_full = filter(tbl_lt60_30, !str_detect(label, 'base')),
  overall_by_age_full = filter(tbl_overall_by_age, !str_detect(label, 'base')),
  comorb_full = filter(tbl_comorb, !str_detect(label, 'base'))
  
) %>% 
  map(
    .f = function(tbl){
      tbl %>% 
        as_grouped_data(groups = 'label') %>%
        as_flextable(hide_grouplabel = TRUE) %>% 
        add_header_row(
          values = c("", bp_cat_descr, names(tbl)[8]), 
          colwidths = c(2, 4, 1)
        ) %>% 
        theme_box() %>% 
        set_header_labels(
          'pce_var' = 'PCE',
          'prevent_var' = 'PREVENT'
        ) %>% 
        padding(i = ~is.na(label), 
                j = 1, 
                padding.left = 10, 
                part = 'body') %>% 
        height(height = 1.5, part = 'header') %>%
        width(width = 1.25) %>%
        width(j = 1:6, width = 1.1) %>% 
        align(align = 'center', part = 'all') %>%
        align(j = 1, align = 'left', part = 'all') %>%
        # add_footer_lines(value = as_paragraph(abbrvs)) %>% 
        merge_v(part = 'header') %>% 
        table_polisher()
    })

tbls_risk_cross$overall_base
```


```{r}
block_section(
  prop_section(
    page_size = page_size(orient = "landscape"),
    page_margins = page_mar(bottom = 1/8, top = 1/8,
                            right = 1/4, left = 1/4),
    type = "continuous"
  )
)
```

Table 4: Prevalence ratios for 10-year total cardiovascular disease risk ≥ 15% on the PREVENT base equation among US adults with 10-year atherosclerotic cardiovascular disease risk ≥ 10% by the Pooled Cohort equations and systolic blood pressure of 130-139 mm Hg or diastolic blood pressure of 80-89 mm Hg.

```{r}

tbls_discrepant <- analysis_overall %>% 
  getElement("tbl_discrepant_overall") %>% 
  split(.$bp_cat_meds_included) %>% 
  map(
    .f = ~ {
      
      .x %>% 
        select(-bp_cat_meds_included) %>% 
        as_grouped_data(groups = 'label') %>%
        remove_empty('rows') %>% 
        as_flextable(hide_grouplabel = TRUE) %>% 
        add_header_row(
          values = c(" ", "Prevalence ratio (95% CI)"),
          colwidths = c(3, 2)
        ) %>%
        theme_box() %>% 
        set_header_labels(
          level = "Characteristic",
          'pr_unadj' = 'Unadjusted',
          'pr_adj' = 'Adjusted'
        ) %>% 
        padding(i = 4:7, j = 1, 
                padding.left = 10, 
                part = 'body') %>% 
        height(height = 1.5, part = 'header') %>%
        width(width = 1.1) %>%
        width(j = 1, width = 2) %>% 
        align(align = 'center', part = 'all') %>%
        align(j = 1, align = 'left', part = 'all') %>%
        # add_footer_lines(value = as_paragraph(abbrvs)) %>% 
        merge_v(part = 'header') %>% 
        footnote(
          i = 1, 
          j = 4,
          part = 'header', 
          value = as_paragraph("Prevalence ratios for continuous variables are per 5 years of age, per 40 mg/dL of total cholesterol, 20 mg/dL of HDL cholesterol, 20 mg/dL of non-HDL cholesterol, per 5 ml/min/1.73 m2 of estimated glomerular filtration rate, per 1 log mg/g of albumin-to-creatinine ratio, 10 mm Hg of systolic blood pressure, 5 mm Hg of diastolic blood pressure."),
          ref_symbols = fts[2]
        ) %>% 
        footnote(
          i = 2,
          j = 1,
          part = 'header',
          value = as_paragraph(value_note),
          ref_symbols = fts[3]
        ) %>% 
        footnote(
          i = 2, 
          j = 5, 
          value = as_paragraph("Adjusted for age and sex."),
          ref_symbols = fts[4],
          part = 'header'
        ) %>% 
        add_footer_lines(value = as_paragraph(abbrvs)) %>%
        table_polisher()
      
    }
  )

tbls_discrepant$`130-139/80-89`

```


```{r}

block_section(
  prop_section(
    page_size = page_size(orient = "portrait"),
    type = "continuous",
    page_margins = margins_normal
  )
)

```

Table 5. Mean 30-year predicted total cardiovascular disease risk estimated by the PREVENT equations within level of predicted atherosclerotic and total cardiovascular disease 10-year risk categories by blood pressure category among adults 30 to <60 years of age.  

```{r}

tbls_risk_cross$lt60_30_base

```

\newpage

Table 6. Mean 10-year and 30-year risk by characteristics of US adults with stage 1 hypertension. Mean 30-year risk is further restricted to US adults aged 30 to < 60 years.

```{r}

meandiffs_orig <- analysis_overall %>%
  getElement("tbl_mean_diff_overall")

meandiffs_age_lt60 <- analysis_lt60 %>% 
  getElement("tbl_mean_diff_age_lt60")

tbls_meandiffs <- map2(
  .x = meandiffs_orig,
  .y = meandiffs_age_lt60,
  .f = ~ {
    
    overall <- .x %>% 
      filter(outcome != "cvd_prevent_30_base")

    age_lt60 <- .y %>% 
      filter(outcome == "cvd_prevent_30_base")
    
    bind_rows(overall, age_lt60) %>% 
      filter(level != "Other") %>% 
      mutate(across(where(is.numeric), ~.x * 100)) %>% 
      transmute(
        outcome, label, level,
        tbv_est = table_glue(
          "{estimate}\n({ci_lower}, {ci_upper})"
        ),
        tbv_diff = if_else(
          estimate_diff == 0,
          "0 (ref)",
          table_glue(
            "{estimate_diff}\n({ci_lower_diff}, {ci_upper_diff})"
          )
        ) 
      ) %>% 
      pivot_wider(names_from = outcome, 
                  values_from = c(tbv_est, tbv_diff)) %>% 
      select(label, level, 
             tbv_est_ascvd_pce, 
             tbv_diff_ascvd_pce,
             tbv_est_ascvd_prevent_base, 
             tbv_diff_ascvd_prevent_base,
             tbv_est_cvd_prevent_base, 
             tbv_diff_cvd_prevent_base,
             tbv_est_cvd_prevent_30_base, 
             tbv_diff_cvd_prevent_30_base) %>% 
      as_grouped_data(groups = "label") %>% 
      as_flextable(hide_grouplabel = TRUE) %>% 
      theme_box() %>%
      add_header_row(
        values = c("Characteristic",
                   "Pooled cohort equations",
                   "PREVENT equations"),
        colwidths = c(1, 2, 6)
      ) %>% 
      width(width = 1.1) %>%
      width(j = 1, width = 2) %>%
      align(align = 'center', part = 'all') %>%
      align(j = 1, align = 'left', part = 'all') %>%
      padding(i = ~is.na(label),
              j = 1,
              padding.left = 15, 
              part = 'body') %>% 
      set_header_labels(
        level = "Characteristic",
        tbv_est_ascvd_pce = "10-year ASCVD risk",
        tbv_diff_ascvd_pce = "Difference",
        tbv_est_ascvd_prevent_base = "10-year ASCVD risk",
        tbv_diff_ascvd_prevent_base = "Difference",
        tbv_est_cvd_prevent_base = "10-year total CVD risk",
        tbv_diff_cvd_prevent_base = "Difference",
        tbv_est_cvd_prevent_30_base = "30-year total CVD risk",
        tbv_diff_cvd_prevent_30_base = "Difference"
      ) %>% 
      footnote(
        i = 2, 
        j = c("tbv_diff_ascvd_pce",
              "tbv_diff_ascvd_prevent_base",
              "tbv_diff_cvd_prevent_base",
              "tbv_diff_cvd_prevent_30_base"),
        part = 'header', 
        value = as_paragraph("Adjusted for age and sex"),
        ref_symbols = fts[1]
      ) %>% 
      merge_v(part = 'header') %>% 
      table_polisher()
    
    
  }
)


tbls_meandiffs$`130-139/80-89`

```



```{r}
block_section(
  prop_section(
    page_size = page_size(orient = "landscape"),
    page_margins = page_mar(bottom = 1/8, top = 1/8,
                            right = 1/4, left = 1/4),
    type = "continuous"
  )
)
```

\newpage

Figure 1: Cross-categorization of 10-year atherosclerotic cardiovascular disease risk, 10-year total cardiovascular disease risk, and 30-year total cardiovascular disease risk.

```{r dpi=300, fig.width=11, fig.height=6}

analysis_overall %>%
  getElement("tbl_risk_flow_overall") %>%
  relocate(p_1, .after = ascvd_pce_bnry_10) %>% 
  relocate(p_2, .after = cvd_prevent_base_bnry_15) %>% 
  # mutate(across(starts_with("p_"), ~table_value(.x * 100))) %>%
  as_grouped_data("bp_cat_meds_included") %>%
  as_flextable(hide_grouplabel = TRUE) %>%
  merge_v(j = c(2:7), part = 'body') %>%
  theme_box() %>%
  width(width = 1.1) %>%
  width(j = 1, width = 2) %>%
  align(align = 'center', part = 'all') %>%
  align(j = 1, align = 'left', part = 'all') %>%
  set_header_labels(
    ascvd_pce_bnry_10 = "PCEs",
    cvd_prevent_base_bnry_15 = "PREVENT 10-year CVD",
    cvd_prevent_30_base_bnry_30 = "PREVENT 30-year CVD",
    p_1 = "%",
    p_2 = "%",
    p_3 = "%"
  ) %>% 
  table_polisher()

  

# tar_load(tbl_risk_flow_overall)

# require(sankey)
# require(magrittr)
# 
# tbl_risk_flow_overall <- analysis_overall %>%
#   getElement("tbl_risk_flow_overall") %>% 
#   filter(bp_cat_meds_included == '130-139/80-89') %>% 
#   ungroup() %>% 
#   select(-bp_cat_meds_included)
# 
# wts_1 <- tbl_risk_flow_overall %>%
#   select(1:2) %>%
#   distinct() %>%
#   transmute(V1 = "US Adults\n30-79 years",
#             V2 = paste("PCE 10-year\nASCVD risk", 
#                        ascvd_pce_bnry_10),
#             weight = p_1)
# 
# wts_2 <- tbl_risk_flow_overall %>%
#   select(1, 3:4) %>%
#   distinct() %>%
#   transmute(V1 = paste("PCE 10-year\nASCVD risk", 
#                        ascvd_pce_bnry_10),
#             V2 = paste("PREVENT 10-year\nCVD risk", cvd_prevent_base_bnry_15),
#             weight = p_2)
# 
# wts_3 <- tbl_risk_flow_overall %>%
#   filter(ascvd_pce_bnry_10 == '≥ 10%') %>% 
#   select(3, 5:6) %>%
#   distinct() %>%
#   transmute(V1 = paste("PREVENT 10-year\nCVD risk",
#                        cvd_prevent_base_bnry_15),
#             V2 = paste("PREVENT 30-year\nCVD risk",
#                        cvd_prevent_30_base_bnry_30),
#             weight = p_3) %>%
#   group_by(V1, V2) %>%
#   summarize(weight = sum(weight))
# 
# 
# wts <- bind_rows(wts_3, wts_2, wts_1)
# 
# sankey_key <- tribble(
#   ~ V1                 , ~V2,
#   "US Adults\n30-79 years" , "PCE 10-year\nASCVD risk < 10%",
#   "US Adults\n30-79 years" , "PCE 10-year\nASCVD risk ≥ 10%",
#   # "PCE 10-year\nASCVD risk < 10%" , "PREVENT 10-year\nCVD risk < 15%",
#   # "PCE 10-year\nASCVD risk < 10%" , "PREVENT 10-year\nCVD risk ≥ 15%",
#   "PCE 10-year\nASCVD risk ≥ 10%" , "PREVENT 10-year\nCVD risk < 15%",
#   "PCE 10-year\nASCVD risk ≥ 10%" , "PREVENT 10-year\nCVD risk ≥ 15%",
#   "PREVENT 10-year\nCVD risk < 15%", "PREVENT 30-year\nCVD risk < 30%",
#   "PREVENT 10-year\nCVD risk < 15%", "PREVENT 30-year\nCVD risk ≥ 30%",
#   # "PREVENT 10-year\nCVD risk ≥ 15%", "PREVENT 30-year\nCVD risk < 30%",
#   "PREVENT 10-year\nCVD risk ≥ 15%", "PREVENT 30-year\nCVD risk ≥ 30%"
# ) %>%
#   as.data.frame() %>%
#   left_join(wts) %>%
#   make_sankey(edges = .)
# 
# new_sizes <- sankey_key$edges %>%
#   group_by(V2) %>%
#   summarize(size = sum(weight)) %>%
#   add_row(V2 = "US Adults\n30-79 years",
#           size = 1) %>%
#   rename(id = V2)
# 
# sankey_key$nodes$size <- NULL
# 
# sankey_key$nodes %<>% left_join(new_sizes)
# 
# sankey_key$nodes$texty[1] <- -.65
# 
# sankey_key$nodes$texty[2] <- -1.35
# sankey_key$nodes$textx[2] <- 0.9
# sankey_key$nodes$pos[2] <- 4
# 
# 
# sankey_key$nodes$texty[3] <- -.4
# sankey_key$nodes$textx[3] <- 1.1
# sankey_key$nodes$pos[3] <- 4
# 
# sankey_key$nodes$texty[4] <- -.93
# sankey_key$nodes$textx[4] <- 1.88
# sankey_key$nodes$pos[4] <- 4
# 
# sankey_key$nodes$texty[5] <- -.37
# sankey_key$nodes$textx[5] <- 1.88
# sankey_key$nodes$pos[5] <- 4
# 
# sankey_key$nodes$texty[6] <- -.8
# sankey_key$nodes$texty[7] <- -.45
# 
# sankey_key$nodes$col <- c("lightseagreen",
#                           "orangered",
#                           "lightseagreen",
#                           "orangered",
#                           "lightseagreen",
#                           "orangered",
#                           "lightseagreen")
# 
# 
# make_sankey(nodes = sankey_key$nodes,
#             edges = sankey_key$edges, 
#             gravity = 'center') %>%
#   sankey()

```


```{r}
block_section(
  prop_section(
    page_size = page_size(orient = "landscape"),
    page_margins = page_mar(bottom = 1/8, top = 1/8,
                            right = 1/4, left = 1/4),
    type = "continuous"
  )
)
```

**SUPPLEMENT**

\newpage

Supplemental Figure 1: Participant cascade

```{r}

nhanes_excluded$counts %>% 
  flextable() %>% 
  theme_box() %>% 
  set_header_labels(
    'label' = 'Inclusion criteria',
    overall = "Total"
  ) %>% 
  width(width = 1.25) %>%
  width(j = 2:5, width = 1.1) %>% 
  align(align = 'center', part = 'all') %>%
  align(j = 1, align = 'left', part = 'all') %>% 
  table_polisher()

```

\newpage

Supplemental Table 1: Distribution of 10-year predicted risk by blood pressure levels and antihypertensive medication use based on the 2013-2020 National Health and Nutrition Examination Survey.

```{r}

tbls_dist$supp %>% 
  footnote(
    i = c(7, 13), 
    j = 1,
    part = 'body', 
    ref_symbols = fts[1],
    value = as_paragraph(
      'Incorporates information on glycated hemoglobin and albumin-to-creatinine ratio'
    )
  )

```


```{r}

block_section(
  prop_section(
    page_size = page_size(orient = "portrait"),
    type = "continuous",
    page_margins = margins_normal
  )
)

```

Supplemental Table 2: Cross-categorization of 10-year predicted risk by the pooled cohort equations and PREVENT equations after excluding people age ≥65 years, with diabetes or chronic kidney disease (ACR > 30 mg/g or eGFR < 60 ml/min/1.73 m2).

```{r}
tbls_risk_cross$comorb_base
```


\newpage

Supplemental Table 3: Cross-categorization of 10-year predicted risk by the pooled cohort equations and PREVENT equations among US adults < 60 years of age and ≥ 60 years of age.

```{r}

tbls_risk_cross$overall_by_age_base

```

\newpage

Supplemental Table 4. Mean 10-year and 30-year risk by characteristics of US adults with systolic blood pressure of < 120 mm Hg and diastolic blood pressure < 80 mm Hg. Mean 30-year risk is further restricted to US adults aged 30 to < 60 years.

```{r}

tbls_meandiffs$`<120/80`

```

\newpage

Supplemental Table 5. Mean 10-year and 30-year risk by characteristics of US adults with systolic blood pressure of 120 to 129 mm Hg and diastolic blood pressure < 80 mm Hg. Mean 30-year risk is further restricted to US adults aged 30 to < 60 years.

```{r}

tbls_meandiffs$`120-129/<80`

```

Supplemental Table 6. Mean 10-year and 30-year risk by characteristics of US adults with systolic blood pressure of ≥ 140 mm Hg or diastolic blood pressure ≥ 90 mm Hg. Mean 30-year risk is further restricted to US adults aged 30 to < 60 years.

```{r}

tbls_meandiffs$`≥140/90`

```


\newpage

Supplemental Table 7. Mean 10-year and 30-year risk by characteristics of US adults taking antihypertensive medication. Mean 30-year risk is further restricted to US adults aged 30 to < 60 years.

```{r}
tbls_meandiffs$`Taking antihypertensive medication`
```


```{r}
block_section(
  prop_section(
    page_size = page_size(orient = "landscape"),
    page_margins = page_mar(bottom = 1/8, top = 1/8,
                            right = 1/4, left = 1/4),
    type = "continuous"
  )
)
```
